---
title: "P8105 HW1 - Sophie Gakis (sig2127)"
output: github_document
date: "2026-09-22"
---
# Problem 1 

After downloading the package that contains the penguins dataset (done once in the console), this will load it. Also loading the tidyverse library at the top of the document here. 

```{r}
library (tidyverse)
data("penguins", package = "palmerpenguins")

penguins
```

## The penguins dataset description 

*   Data in the dataset
    * Species (Adelie, Chinstrap, or Gentoo)
    * Island (Biscoe, Dream, or Torgersen)
    * Bill length in mm (Range from 32.1 to 59.6 mm)
    * Bill Dept in mm (Range from 13.1 to 21.5 mm)
    * Flipper length in mm (Range from 172 to 231)
    * Body mass in g (Range from 2,700, 6,300)
    * Sex (Male or Female)
    * Year (2007 to 2009)
    
*   Size of the dataset
```{r}
nrow(penguins)
ncol(penguins)
```

*   The mean flipper length: `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)`

## Making a scatter plot 

```{r}
scatterplot_1 = ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point() 

scatterplot_1
```

## Saving the scatterplot 

```{r}
ggsave("scatterplot_1.png", plot = scatterplot_1)
```

# Problem 2 

## Creating the specified data frame 

```{r}
problem_2_df = 
  tibble(
  rand_sampl = rnorm(10),
  log_vec = rand_sampl > 0,
  char_vec = letters[1:10],
  fact_vec = factor(sample(c("Level 1", "Level 2", "Level 3"), 10, replace = TRUE))
  )

problem_2_df
```

## Trying to take the mean of each variable in the dataframe 

* Mean of random sample: `r round(mean(pull(problem_2_df, rand_sampl)), 2)`

* Mean of logical vector: `r round(mean(pull(problem_2_df, log_vec)), 2)`

* Mean of character vector: `r round(mean(pull(problem_2_df, char_vec)), 2)`

* Mean of factor vector: `r round(mean(pull(problem_2_df, fact_vec)), 2)`

Using the code above to take the mean of each variable in my problem_2_df, it seems like the 
mean for the random sample and the logical vector did work, while the mean for the character vector and the factor vector did not work. I think that is becuase they are currently formatted as character variables and not numeric variables, so the means cannot be taken. 


