---
title: "P8105 HW1 - Sophie Gakis (sig2127)"
output: github_document
date: "2026-09-22"
---
# Problem 1 

## After downloading the package that contains the penguins dataset (done once in the console), this will load it. Also loading the tidyverse library at the top of the document here. 

```{r}
library (tidyverse)
data("penguins", package = "palmerpenguins")

penguins
```

## The penguins dataset description 

*   Data in the dataset
    * Species (Adelie, Chinstrap, or Gentoo)
    * Island (Biscoe, Dream, or Torgersen)
    * Bill length in mm (Range from 32.1 to 59.6 mm)
    * Bill Dept in mm (Range from 13.1 to 21.5 mm)
    * Flipper length in mm (Range from 172 to 231)
    * Body mass in g (Range from 2,700, 6,300)
    * Sex (Male or Female)
    * Year (2007 to 2009)
    
*   Size of the dataset
```{r}
nrow(penguins)
ncol(penguins)
```
  
*   The mean flipper length: `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)`

## Making a scatter plot 

```{r}
scatterplot_1 = ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point() 

scatterplot_1
```

## Saving the scatterplot 

```{r}
ggsave("scatterplot_1.png", plot = scatterplot_1)
```


